---
title: "BDS Main Analyses"
author: "jeryl_lim"
date: '2022-11-01'

---
### Load packages

```{r,echo=FALSE}

## Data wrangling
library(dplyr)   
library(tidyr)
library(readxl)      # required for read_excel() method
library(data.table)


## Visualisation libraries
library(ggplot2)
library(visreg)
library(ggsignif)    # For significance bars on ggplots

library(egg)         # required for ggarrange (panelling multiple ggplots)

## Modelling
library(lme4)        # required for `lmer() and glmer()` methods
library(lmerTest)    # required for p-value approximations
library(performance) # check for collinearity using check_collinearity()

library(emmeans)     # required to retrieve least-square estimates, using `lsmeans()` and `emmeans`


library(aod)         # required to call model comparison methods, such as `AIC`, `BIC`
library(car)         # required for Chi-square test of Coefficient Equality `linearHypothesis`
library(MuMIn)       # required for r.squaredGLMM() function
library(performance) # required for check_collinearity function
library(sjPlot)      # required for `tab_model(model)`, which provides a formatted output of the model in APA style.

library(DHARMa)      # required for residual inspection


# Source helper functions script
source("helper-functions.R")


# # Other reserve libraries
# library(piecewiseSEM)


# Turn off scientific notation
options(scipen = 20)

```

---

# Data Management

```{r,echo=FALSE}

# Read bds.data
bds.data <- as.data.table(read.csv("../data/exp2_BDS_study_data/data_master.csv"))

# Check for duplicates
bds.data[duplicated(bds.data),]


```



## Factorize and label Condition and Session

```{r,echo=FALSE}
# Convert Condition to factor

bds.data$Condition   <- factor(bds.data$Condition,
                               levels = c(1, 2, 3), labels = c("WR", "SR", "CM")
                               )

# convert Session to factor
bds.data$SessionTime <- factor(bds.data$SessionTime,
                               levels = c(1,2), labels = c("AM", "PM")
                               )


```


```{r, echo=FALSE}

# Read in data
bds.temp.csl <- read_excel("../data/exp2_BDS_study_data/cumulative_sleep_lost_tabulation.xlsx", sheet= 1)

# Create new cumulativeSleepLost variable in the main dataset
bds.data$cumulativeSleepLost = NA

# Merge cumulative sleep loss into respective participants in master dataset

for (id in unique(bds.data[bds.data$Condition == "SR", ]$PtID)){
  bds.data[bds.data$PtID == id, "cumulativeSleepLost"] = bds.temp.csl[bds.temp.csl$ID == id, "cumulativeSleepLost"]
}

# Clear bds.temp.csl from global
rm(bds.temp.csl)

```

## Subset bds.data

```{r,echo=FALSE}

# -----------------------------------------------------------------------
# Subset bds.data into SR and CM
# -----------------------------------------------------------------------
bds.data.WRSR    =  subset(bds.data, Condition == 'WR'|Condition == 'SR')
bds.data.WRCM    =  subset(bds.data, Condition == 'WR'| Condition == 'CM')

# -----------------------------------------------------------------------
# Split each subset further into AM and PM sessions
# -----------------------------------------------------------------------

bds.data.WRSR.AM = subset(bds.data.WRSR, SessionTime == 'AM')
bds.data.WRSR.PM = subset(bds.data.WRSR, SessionTime == 'PM')
bds.data.WRCM.AM = subset(bds.data.WRCM, SessionTime == 'AM')
bds.data.WRCM.PM = subset(bds.data.WRCM, SessionTime == 'PM')


# -----------------------------------------------------------------------
# Create subset of bds.data.WRSR and bds.data.WRCM without the NoBrainers
# -----------------------------------------------------------------------
bds.data.WRSR.exNB    <- subset(bds.data.WRSR, NoBrainers == 0 )
bds.data.WRCM.exNB    <- subset(bds.data.WRCM, NoBrainers == 0 )
# Split each subset into AM and PM sessions
bds.data.WRSR.AM.exNB <- subset(bds.data.WRSR.exNB, SessionTime == 'AM')
bds.data.WRSR.PM.exNB <- subset(bds.data.WRSR.exNB, SessionTime == 'PM')
# Split each subset into AM and PM sessions
bds.data.WRCM.AM.exNB <- subset(bds.data.WRCM.exNB, SessionTime == 'AM')
bds.data.WRCM.PM.exNB <- subset(bds.data.WRCM.exNB, SessionTime == 'PM')

# -----------------------------------------------------------------------
# Create subset of SR/CM bds.data with HARD trials
# -----------------------------------------------------------------------
bds.data.WRSR.hard    <- subset(bds.data.WRSR, IsEasy == 0)
bds.data.WRCM.hard    <- subset(bds.data.WRCM, IsEasy == 0)
# Split each subset into AM and PM sessions
bds.data.WRSR.hard.AM <- subset(bds.data.WRSR.hard, SessionTime == 'AM')
bds.data.WRSR.hard.PM <- subset(bds.data.WRCM.hard, SessionTime == 'PM')
# Split each subset into AM and PM sessions
bds.data.WRCM.hard.AM <- subset(bds.data.WRCM.hard, SessionTime == 'AM')
bds.data.WRCM.hard.PM <- subset(bds.data.WRCM.hard, SessionTime == 'PM')

```


---

# Demographics

```{r}

# Create tibble for demographics
bds.data.demographics        <- tibble(.rows = 41)
bds.data.demographics$PtID   <- unique(bds.data.WRSR.exNB$PtID)
bds.data.demographics$sex    <- NA
bds.data.demographics$age    <- NA


# Read in original demographic dataframe and store in a temporary dataframe
bds.temp.demographics  <- read_excel("../data/exp2_BDS_study_data/1_Demographics.xlsx")

# Pull demographic data from original demographic dataframe
for (id in bds.data.demographics$PtID){
  bds.data.demographics[bds.data.demographics$PtID == id, "sex"] <- bds.temp.demographics[bds.temp.demographics$ID == id, "Sex"]
  bds.data.demographics[bds.data.demographics$PtID == id, "age"] <- bds.temp.demographics[bds.temp.demographics$ID == id, "Age"]
};

# Remove temporary dataframe
rm(bds.temp.demographics)


```



---

# Analyses 

### Count number of participants who were assigned SR

```{r}

length(unique(
  bds.data.WRSR[bds.data.WRSR$Condition == 'SR',]$PtID
));


```

## Manipulation Check model (KSS)

```{r}

# Subset only necessary variables
bds.data.WRSR.KSS <-bds.data.WRSR[c("PtID", "SessionTime", "Condition", "StartKSS")]

# Keep unique values
bds.data.WRSR.KSS <- distinct(bds.data.WRSR.KSS)


```

### Normality check of StartKSS variable

```{r,echo=FALSE}

# Density plot
plot.bds.KSS.density <- ggplot(bds.data.WRSR.KSS, aes(x = StartKSS)) + geom_density()

# Shapiro-Wilk test   
shapiro.test(bds.data.WRSR.KSS$StartKSS)

# ---------------------------------------------------------------------
# Both density plots and Shapiro-wilk test indicate non-normality
# Here we try to apply non-linear transformations (not used in final manuscript)
# ---------------------------------------------------------------------

# Square-root transformation
bds.data.WRSR.KSS$sqrtKSS <- sqrt(bds.data.WRSR.KSS$StartKSS)

# inspect plot
plot.bds.sqrtKSS.density <- ggplot(bds.data.WRSR.KSS, aes(x = sqrtKSS)) + geom_density()

# Shapiro test
shapiro.test(bds.data.WRSR.KSS$sqrtKSS)

```



## KSS Manipulation Check model

```{r,echo=FALSE}

# Create model
m.bds.KSS <- lmer(StartKSS ~ 1 + SessionTime*Condition + (1|PtID),
               data = bds.data.WRSR.KSS)

m.bds.KSS1 <- lmer(StartKSS ~ 1 + SessionTime + Condition + (1|PtID),
               data = bds.data.WRSR.KSS)
m.bds.KSS2 <- lmer(StartKSS ~ 1 + SessionTime*Condition + (1|PtID),
               data = bds.data.WRSR.KSS)

anova(m.bds.KSS1, m.bds.KSS2)

# Follow up models using separate AM and PM data
bds.data.WR.KSS <- bds.data.WRSR.KSS[bds.data.WRSR.KSS$Condition == "WR",]
bds.data.SR.KSS <- bds.data.WRSR.KSS[bds.data.WRSR.KSS$Condition == "SR",]

# Model of AM only
m.bds.KSS.WR <- lmer(StartKSS ~ 1 + SessionTime + (1|PtID),
                     data = bds.data.WR.KSS)

m.bds.KSS.SR <- lmer(StartKSS ~ 1 + SessionTime + (1|PtID),
                     data = bds.data.SR.KSS)


summary(m.bds.KSS); lm.beta.lmer(m.bds.KSS); confint(m.bds.KSS, method = "Wald")

# Get R-squared
r.squaredGLMM(m.bds.KSS)

# Check collinearity
check_collinearity(m.bds.KSS)

# Model output in APA style
tab_model(m.bds.KSS,
          show.est = TRUE,
          show.se = TRUE,
          string.se = "SE",
          string.ci = "95% CI",
          string.est = "Estimate"
          )
```

#### Inspect Residuals via Residual plots

```{r,echo=FALSE}
sim_output <- simulateResiduals(m.bds.KSS, plot = F); plotQQunif(sim_output); plotResiduals(sim_output)

```

#### Plot the graphs of KSS least-square estimates

``` {r, echo = FALSE}

# lsmeans of pooled model with SessionTime x Condition interaction [do not use]
bds.data.KSS.lsmeans <- as_tibble(
  lsmeans(m.bds.KSS, spec = c("Condition", "SessionTime", by = c("SessionTime")
                           ))
  )

# Get lsmeans from each follow-up model
bds.data.WR.KSS.lsmeans <- as_tibble(
  lsmeans(m.bds.KSS.WR, spec = "SessionTime")
  ) %>% mutate(Condition = "WR")
bds.data.SR.KSS.lsmeans <- as_tibble(
  lsmeans(m.bds.KSS.SR, spec = "SessionTime")
) %>% mutate(Condition = "SR")

# Bind into one tibble
bds.data.KSS.lsmeans <- rbind(bds.data.WR.KSS.lsmeans, bds.data.SR.KSS.lsmeans)%>% mutate(Condition = factor(Condition, levels = c("WR", "SR")))


bds.plot.KSS.lsmeans <- ggplot(bds.data.KSS.lsmeans, aes(x = SessionTime, y = lsmean, group = Condition)) +
  geom_line(aes(color = Condition)) +
  geom_point(size = 2 , aes(color= Condition)) +
  scale_color_manual(values = c("blue", "red")) +
  scale_shape_manual(values = c(17, 19)) +
  scale_y_continuous(limits = c(2, 7)) +
  geom_errorbar(aes(ymin = bds.data.KSS.lsmeans$lower.CL, ymax = bds.data.KSS.lsmeans$upper.CL, color = Condition),  width = 0.1) + 
  theme_classic() + 
  theme(
    aspect.ratio = 0.9, 
    axis.title = element_text(size = 18), axis.text = element_text(size = 15), 
    axis.line = element_line(colour = 'black', linewidth = 2),
    legend.title = element_text(size = 15), legend.text = element_text(size = 12)
    )


# fill = c("#999DA0", "#777B7E", "#C7C6C1")
bds.plot.KSS.lsmeans <- ggplot(bds.data.KSS.lsmeans, aes(x = SessionTime, y =  lsmean, fill= Condition, label = lsmean)) +
  geom_bar( position = position_dodge(), stat = "identity", color = "black", linewidth = 1) +
  
  scale_fill_manual(values = c("#F1F1F1", "#7B7B7B")) +
  scale_y_continuous(limits = c(0, 8)) +
  labs(x = "Session Time", y = "KSS score") + 
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), color = "#222021", width = 0.2, linewidth = 1, position = position_dodge(.9))+
  theme_pubr() +  # theme_classic() +
  theme(aspect.ratio = 1, axis.line = element_line(colour = 'black', linewidth = 2), axis.title = element_text(size = 20), axis.text = element_text(size = 20), legend.title  = element_text(size = 18), legend.text = element_text(size = 18)) 
  # geom_text(aes(label = round(lsmean, 2)), position = position_dodge(1), vjust = -5, size = 5.5)

# Save as png with transparent background
ggsave(
  plot = bds.plot.KSS.lsmeans,
  filename = "../img/bds/BDS_KSS_score.png",
  bg = "transparent"
  )


```


## Accuracy model

```{r,echo=FALSE}

bds.data.WRSR.exNB$entropy <- 0

for (row_x in 1:nrow(bds.data.WRSR.exNB)){
  prob1 <- bds.data.WRSR.exNB[row_x, "post_prob"]
  prob2 <- 1-prob1
  bds.data.WRSR.exNB[row_x, "entropy"] <- calc_entropy(c(prob1, prob2))
}



# Accuracy model excluding NoBrainer trials
m.bds.ACC1<-glmer(
  IsCorrect~ 1 + Order + entropy  + Condition  +  SessionTime + (1|PtID),
  family = binomial("logit"),
  bds.data.WRSR.exNB
  );

m.bds.ACC2<-glmer(
  IsCorrect~ 1 + Order + entropy + Condition*SessionTime + (1|PtID),
  family = binomial("logit"),
  bds.data.WRSR.exNB
  );

m.bds.ACC3<-glmer(
  IsCorrect~ 1 + Order + entropy*Condition*SessionTime + (1|PtID),
  family = binomial("logit"),
  bds.data.WRSR.exNB
  );


# Model comparisons
anova(m.bds.ACC1, m.bds.ACC2, m.bds.ACC3)

# Model output in APA style
tab_model(
  m.bds.ACC1,
  transform = NULL,  #Uncomment if raw log odds estimates needed
  show.est = TRUE,
  show.se = TRUE,
  string.se = "SE",
  string.ci = "95% CI",
  # string.est = "Estimate",
  digits = 3
);

# Get marginal mean probabilities
 emmeans(m.bds.ACC1, 
         spec = c("Condition", "SessionTime"),  
         by = c("Condition"), type = "response"
         );

bds.data.ACC <- as_tibble(bds.data.ACC);   # Coerce to tibble


# Plot accuracy least-square estimates
plot.bds.ACC <- ggplot(bds.data.ACC, aes(x = Condition, y = prob, color = SessionTime )) + 
  geom_point(size = 3) +
  scale_y_continuous(limits = c(0.5, 1)) +
  labs( x = "Condition", y = "Probability of Accurate Response", color = "Session") +
  scale_color_manual(values = c("black", "black")) + 
  geom_errorbar(aes(ymin = bds.data.ACC$asymp.LCL, ymax = bds.data.ACC$asymp.UCL), color = '#595959', width = 0.1) + 
  theme_bw()+
  theme(aspect.ratio = 1.5, axis.title = element_text(size=18), axis.text=element_text(size=15),
        legend.title=element_text(size=15), legend.text=element_text(size =12))



# Facet wrap the plot
plot.bds.ACC <- plot.bds.ACC + facet_wrap(~SessionTime, ncol = 2) +theme(strip.text = element_text(size = 15));  

# Save as png with transparent background
# ggsave(
#   plot = plot.bds.ACC,
#   filename = "img/bds/BDS_trial_accuracy.png",
#   bg = "transparent"
#   )

 
```

### Check Residuals

```{r,echo=FALSE}
sim_output <- simulateResiduals(m.bds.ACC1, plot = F); plotQQunif(sim_output); plotResiduals(sim_output)

```

---

# Decision Weight Models

## Analyses Excluding NoBrainer Trials

### Pooled SR Model without the NoBrainer trials 

Note: Convergence issue on this model

```{r,echo=FALSE}

m.bds.WRSR.AMPM.exNB <- glmer(
  PtResp ~ 1 + SessionTime*Condition*LogLLA + SessionTime*Condition*LogBaserate + (1|PtID),
  family = binomial('probit'),
  data = bds.data.WRSR.exNB
)

# Convergence error message:
## Warning in checkConv(attr(opt, "derivs"), opt$par, ctrl = control$checkConv,  :
##   Model failed to converge with max|grad| = 0.00726695 (tol = 0.002, component 1)

```

### AM-only model without NoBrainers 

```{r,echo=FALSE}



# Build the probit model

m.bds.WRSR.AM.exNB <- glmer(PtResp ~ 1 + Condition*LogLLA + Condition*LogBaserate + 
                  (1 |PtID),
             family = binomial(link = 'probit'),
             bds.data.WRSR.AM.exNB
             )

# Print summary and confint
summary(m.bds.WRSR.AM.exNB); confint(m.bds.WRSR.AM.exNB, method="Wald",level = 0.95, oldNames="FALSE")
# Get R-squared
r.squaredGLMM(m.bds.WRSR.AM.exNB)
# Check collinearity
check_collinearity(m.bds.WRSR.AM.exNB)

# Model output in APA style
tab_model(
  m.bds.WRSR.AM.exNB,        
  transform = NULL, show.est = TRUE, show.se = TRUE,
  string.se = "SE", string.ci = "95% CI", string.est = "Estimate",
  digits = 3, digits.p = 3, digits.rsq = 3, digits.re = 3
  );

# [EXPERIMENTAL] Create scaled variables for LogLLA and LogBaserate on the standard deviation scale
bds.data.WRSR.AM.exNB$LogLLA_scaled      <- scale(bds.data.WRSR.AM.exNB$LogLLA)
bds.data.WRSR.AM.exNB$LogBaserate_scaled <- scale(bds.data.WRSR.AM.exNB$LogBaserate)

```

#### Check Residuals
```{r,echo=FALSE}

sim_output <- simulateResiduals(m.bds.WRSR.AM.exNB, plot = F); plotQQunif(sim_output); plotResiduals(sim_output)

```


## PM-only model without NoBrainers 
```{r,echo=FALSE}

# Create model
m.bds.WRSR.PM.exNB <- glmer(
  PtResp ~ 1 + Condition*LogLLA + Condition*LogBaserate + (1|PtID),
  family = binomial('probit'),
  bds.data.WRSR.PM.exNB
  );




# Print summary & confint
summary(m.bds.WRSR.PM.exNB); confint(m.bds.WRSR.PM.exNB, method = "Wald");

# Check collinearity
check_collinearity(m.bds.WRSR.PM.exNB)

# Confidence Intervals
confint(m.bds.WRSR.PM.exNB, method="Wald",level = 0.95, oldNames="FALSE")


# Model output in APA style
tab_model(m.bds.WRSR.PM.exNB,
          transform = NULL, show.est = TRUE, show.se = TRUE,
          string.se = "SE", string.ci = "95% CI", string.est = "Estimate",
          digits = 3, digits.p = 3, digits.rsq = 3, digits.re = 3
          );




```

### Check Residuals
```{r,echo=FALSE}

# Check residuals
sim_output <- simulateResiduals(m.bds.WRSR.PM.exNB, plot = F); plotQQunif(sim_output); 

```


---

## Plot Decision Weights across both AM & PM sessions

```{r, echo = FALSE}

# Create placeholder variables and fill with respective data

condition    <- c("WR", "WR", "SR", "SR", "WR", "WR", "SR", "SR");
session      <- c(rep("AM", 4), rep("PM", 4));
information  <- c(rep(c("Evidence", "Base Rate"), 4));

coefficients <- c(0.30879,  0.77677,  0.2452,  0.65133,  0.29171,  0.72799,  0.23351,  0.77166);

se_lower     <- c(0.28761,  0.73181,  0.21407,  0.58405,  0.27113,  0.6843,  0.20264,  0.70358);
se_upper     <- c(0.32997,  0.82173,  0.27633,  0.71861,  0.31229,  0.77168,  0.26438,  0.83974);
ci_lower     <- c(0.2672815, 0.6886429, 0.1841902, 0.5194604, 0.25137681, 0.64235532, 0.17300985, 0.63821854);
ci_upper     <- c(0.350304, 0.864895588, 0.306202423, 0.783197672, 0.332046028, 0.813631264, 0.294015979, 0.905105997);

# Create tibble for Decision Weights
bds.temp.DW  <- tibble(condition, session, information, coefficients, se_lower, se_upper, ci_lower, ci_upper)

bds.temp.DW$condition   <- factor(bds.temp.DW$condition, levels = c("WR","SR"))
bds.temp.DW$session     <- factor(bds.temp.DW$session, levels = c("AM", "PM"))
bds.temp.DW$information <- factor(bds.temp.DW$information, levels = c("Base Rate", "Evidence"))

plot.bds.DW <- ggplot(data = bds.temp.DW, aes( x = condition, y = coefficients , shape =  information)) + 
  geom_point(size= 3) + 
  scale_y_continuous(limits = c(0, 1)) +
  scale_shape_manual(values = c(17, 19))+
  # scale_color_manual(labels = c("Draw Outcome","Base Rate Odds"), values = c("blue", "red"))+
  labs(x = "Condition", y = "Decision Weight", shape = "Information")+
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),linewidth = 1, color = '#595959', width = 0.1)+ # Add error bars
  theme_bw(base_size = 18) + 
  theme(aspect.ratio =  2.4,  axis.title = element_text(size=15), axis.text=element_text(size=15),
        legend.text=element_text(size=15), legend.title = element_text(size = 15))  

# Facet wrap plots
plot.bds.DW <- plot.bds.DW  + facet_wrap(~session, ncol = 2) + 
  theme(strip.text = element_text(size = 15), panel.border = element_rect(linewidth = 2))+ ggtitle("Experiment 2"); 


# Save as png with transparent background
ggsave( plot = plot.bds.DW,
        filename = "../img/bds/BDS_decisionWeights.png",
        bg = "transparent")

# Remove placeholder variables
rm(condition);rm(session);rm(information);rm(coefficients);rm(se_lower);rm(se_upper);rm(ci_lower);rm(ci_upper);rm(bds.temp.DW)

```

---
# RT Analyses

```{r RT-analyses prep}


# Create LLA and LBR strengths
bds.data.WRSR.AM.exNB[, LLAstrength:=as.factor(abs(LogLLA))]
bds.data.WRSR.AM.exNB[, LBRstrength:=as.factor(abs(LogBaserate))]
bds.data.WRSR.PM.exNB[, LLAstrength:=as.factor(abs(LogLLA))]
bds.data.WRSR.PM.exNB[, LBRstrength:=as.factor(abs(LogBaserate))]

# Calculate entropy
bds.data.WRSR.AM.exNB$entropy <- 0
for (row_x in 1:nrow(bds.data.WRSR.AM.exNB)){
  prob1 <- bds.data.WRSR.AM.exNB[row_x, post_prob]
  prob2 <- 1-prob1
  bds.data.WRSR.AM.exNB[row_x, "entropy"] <- calc_entropy(c(prob1, prob2))
}

bds.data.WRSR.PM.exNB$entropy <- 0
for (row_x in 1:nrow(bds.data.WRSR.PM.exNB)){
  prob1 <- bds.data.WRSR.PM.exNB[row_x, post_prob]
  prob2 <- 1-prob1
  bds.data.WRSR.PM.exNB[row_x, "entropy"] <- calc_entropy(c(prob1, prob2))
}

# Create Order variable
bds.data.WRSR.AM.exNB$Order <- ifelse(bds.data.WRSR.AM.exNB$NormalFirst == 1 & bds.data.WRSR.AM.exNB$SessionTime == "AM", 1,
                                   ifelse(bds.data.WRSR.AM.exNB$NormalFirst == 1 & bds.data.WRSR.AM.exNB$SessionTime == "PM", 2, 
                                          ifelse (bds.data.WRSR.AM.exNB$NormalFirst == 0 & bds.data.WRSR.AM.exNB$SessionTime == "AM", 3 , 4)))
bds.data.WRSR.PM.exNB$Order <- ifelse(bds.data.WRSR.PM.exNB$NormalFirst == 1 & bds.data.WRSR.PM.exNB$SessionTime == "PM", 1,
                                   ifelse(bds.data.WRSR.PM.exNB$NormalFirst == 1 & bds.data.WRSR.PM.exNB$SessionTime == "PM", 2, 
                                          ifelse (bds.data.WRSR.PM.exNB$NormalFirst == 0 & bds.data.WRSR.PM.exNB$SessionTime == "PM", 3 , 4)))


# Create Order variable to represent no. of times participant has done the task
bds.data.WRSR.exNB$Order <- ifelse(bds.data.WRSR.exNB$NormalFirst == 1 & bds.data.WRSR.exNB$SessionTime == "AM", 1,
                                   ifelse(bds.data.WRSR.exNB$NormalFirst == 1 & bds.data.WRSR.exNB$SessionTime == "PM", 2, 
                                          ifelse (bds.data.WRSR.exNB$NormalFirst == 0 & bds.data.WRSR.exNB$SessionTime == "AM", 3 , 4)))

# Create log RTs
bds.data.WRSR.AM.exNB[, RT:=as.numeric(RT)]
bds.data.WRSR.AM.exNB[, logRT:=log(RT)]

bds.data.WRSR.PM.exNB[, RT:=as.numeric(RT)]
bds.data.WRSR.PM.exNB[, logRT:=log(RT)]

# Build RT models


m1.bds.AM.rt <-lmer(logRT ~ 1 + entropy + Order + LBRstrength + LLAstrength + (1 |PtID), data = bds.data.WRSR.AM.exNB)
m2.bds.AM.rt <-lmer(logRT ~ 1 + entropy + Order + Condition*LBRstrength + Condition*LLAstrength+ (1 |PtID), data = bds.data.WRSR.AM.exNB)
m3.bds.AM.rt <-lmer(logRT ~ 1 + entropy + Order + Condition*LBRstrength + Condition*LLAstrength+ (Condition |PtID), data = bds.data.WRSR.AM.exNB)
m1.bds.PM.rt <-lmer(logRT ~ 1 + entropy + Order + LBRstrength + LLAstrength + (1 |PtID), data = bds.data.WRSR.PM.exNB)
m2.bds.PM.rt <-lmer(logRT ~ 1 + entropy + Order + Condition*LBRstrength + Condition*LLAstrength+ (1 |PtID), data = bds.data.WRSR.PM.exNB)


# Check model fits
anova(m1.bds.AM.rt, m2.bds.AM.rt, m3.bds.AM.rt )
anova(m1.bds.PM.rt, m2.bds.PM.rt)

# Print model summary of best-fitting models
tab_model(m2.bds.AM.rt, show.se = T, digits = 4)
tab_model(m2.bds.PM.rt, show.se = T, digits = 3)

check_collinearity(m1.bds.AM.rt)


```


Same as NSF analyses, check distribution of black balls presented on trials with max LBR strength


```{r}

# Get distribution of no blk balls on high LBRstrength trials
table(bds.data.WRSR.AM.exNB[LBRstrength == 2.197224577]$NoBlkBall)
table(bds.data.WRSR.PM.exNB[LBRstrength == 2.197224577]$NoBlkBall)

summary(m.bds.bb2)

```

Compared to NSF, trials on BDS with high LBRstrength present LLAstrength across the range and do not deliberately induce high uncertainty in participants. This likely accounts for the opposing results of the RT models when it comes to LBRstrength coefficients. On BDS, high LBR strength tends to be associated with lower reaction times, rather than higher. \


# END

