---
title: "BDS Main Analyses"
author: "jeryl_lim"
date: '2022-11-01'

---
### Load packages

```{r,echo=FALSE}

## Data wrangling
library(dplyr)   
library(tidyr)
library(readxl)      # required for read_excel() method


## Visualisation libraries
library(ggplot2)
library(visreg)
library(ggsignif)    # For significance bars on ggplots

library(egg)         # required for ggarrange (panelling multiple ggplots)

## Modelling
library(lme4)        # required for `lmer() and glmer()` methods
library(lmerTest)    # required for p-value approximations

library(emmeans)     # required to retrieve least-square estimates, using `lsmeans()` and `emmeans`


library(aod)         # required to call model comparison methods, such as `AIC`, `BIC`
library(car)         # required for Chi-square test of Coefficient Equality `linearHypothesis`
library(MuMIn)       # required for r.squaredGLMM() function
library(performance) # required for check_collinearity function
library(sjPlot)      # required for `tab_model(model)`, which provides a formatted output of the model in APA style.

library(DHARMa)      # required for residual inspection

# # Other reserve libraries
# library(piecewiseSEM)


# Turn off scientific notation
options(scipen = 20)

```

---

### Additional function definition
```{r}

# To retrieve standardised coefficients, if needed
lm.beta.lmer <- function(mod) {
   b <- fixef(mod)[-1]
   sd.x <- apply(getME(mod,"X")[,-1],2,sd)
   sd.y <- sd(getME(mod,"y"))
   b*sd.x/sd.y
}

# Calculate standardised Relative Decision Weights
calculate_relative_dw = function(LogLLA, LogBaserate){
  rdw = (LogLLA-LogBaserate)/(LogLLA + LogBaserate);
  return(rdw)
};

```

---
# Data Management

```{r,echo=FALSE}

# Read bds.data
bds.data <- read.csv("./data/BDS_study_data/data_master.csv")

# Check for duplicates
bds.data[duplicated(bds.data),]


```



## Factorize and label Condition and Session

```{r,echo=FALSE}
# Convert Condition to factor

bds.data$Condition   <- factor(bds.data$Condition,
                               levels = c(1, 2, 3), labels = c("WR", "SR", "CM")
                               )

# convert Session to factor
bds.data$SessionTime <- factor(bds.data$SessionTime,
                               levels = c(1,2), labels = c("AM", "PM")
                               )


```


```{r, echo=FALSE}

# Read in data
bds.temp.csl <- read_excel("data/BDS_study_data/cumulative_sleep_lost_tabulation.xlsx", sheet= 1)

# Create new cumulativeSleepLost variable in the main dataset
bds.data$cumulativeSleepLost = NA

# Merge cumulative sleep loss into respective participants in master dataset

for (id in unique(bds.data[bds.data$Condition == "SR", ]$PtID)){
  bds.data[bds.data$PtID == id, "cumulativeSleepLost"] = bds.temp.csl[bds.temp.csl$ID == id, "cumulativeSleepLost"]
}

# Clear bds.temp.csl from global
rm(bds.temp.csl)

```

## Subset bds.data

```{r,echo=FALSE}
# -----------------------------------------------------------------------
# Subset bds.data into SR and CM
# -----------------------------------------------------------------------
bds.data.WRSR    =  subset(bds.data, Condition == 'WR'|Condition == 'SR')
bds.data.WRCM    =  subset(bds.data, Condition == 'WR'| Condition == 'CM')

# -----------------------------------------------------------------------
# Split each subset further into AM and PM sessions
# -----------------------------------------------------------------------

bds.data.WRSR.AM = subset(bds.data.WRSR, SessionTime == 'AM')
bds.data.WRSR.PM = subset(bds.data.WRSR, SessionTime == 'PM')
bds.data.WRCM.AM = subset(bds.data.WRCM, SessionTime == 'AM')
bds.data.WRCM.PM = subset(bds.data.WRCM, SessionTime == 'PM')


# -----------------------------------------------------------------------
# Create subset of bds.data.WRSR and bds.data.WRCM without the NoBrainers
# -----------------------------------------------------------------------
bds.data.WRSR.exNB    <- subset(bds.data.WRSR, NoBrainers == 0 )
bds.data.WRCM.exNB    <- subset(bds.data.WRCM, NoBrainers == 0 )
# Split each subset into AM and PM sessions
bds.data.WRSR.AM.exNB <- subset(bds.data.WRSR.exNB, SessionTime == 'AM')
bds.data.WRSR.PM.exNB <- subset(bds.data.WRSR.exNB, SessionTime == 'PM')
# Split each subset into AM and PM sessions
bds.data.WRCM.AM.exNB <- subset(bds.data.WRCM.exNB, SessionTime == 'AM')
bds.data.WRCM.PM.exNB <- subset(bds.data.WRCM.exNB, SessionTime == 'PM')

# -----------------------------------------------------------------------
# Create subset of SR/CM bds.data with HARD trials
# -----------------------------------------------------------------------
bds.data.WRSR.hard    <- subset(bds.data.WRSR, IsEasy == 0)
bds.data.WRCM.hard    <- subset(bds.data.WRCM, IsEasy == 0)
# Split each subset into AM and PM sessions
bds.data.WRSR.hard.AM <- subset(bds.data.WRSR.hard, SessionTime == 'AM')
bds.data.WRSR.hard.PM <- subset(bds.data.WRCM.hard, SessionTime == 'PM')
# Split each subset into AM and PM sessions
bds.data.WRCM.hard.AM <- subset(bds.data.WRCM.hard, SessionTime == 'AM')
bds.data.WRCM.hard.PM <- subset(bds.data.WRCM.hard, SessionTime == 'PM')

```


---

# Demographics
```{r}

# Create tibble for demographics
bds.data.demographics        <- tibble(.rows = 41)
bds.data.demographics$PtID   <- unique(bds.data.WRSR.exNB$PtID)
bds.data.demographics$sex    <- NA
bds.data.demographics$age    <- NA


# Read in original demographic dataframe and store in a temporary dataframe
bds.temp.demographics  <- read_excel("./data/BDS_study_data/1_Demographics.xlsx")

# Pull demographic data from original demographic dataframe
for (id in bds.data.demographics$PtID){
  bds.data.demographics[bds.data.demographics$PtID == id, "sex"] <- bds.temp.demographics[bds.temp.demographics$ID == id, "Sex"]
  bds.data.demographics[bds.data.demographics$PtID == id, "age"] <- bds.temp.demographics[bds.temp.demographics$ID == id, "Age"]
};

# Remove temporary dataframe
rm(bds.temp.demographics)


```



---

# Manipulation Check and Accuracy

## Count number of participants who did the SR session

```{r,echo=FALSE}

length(unique(
  bds.data.WRSR[bds.data.WRSR$Condition == 'SR',]$PtID
));


```

## [ANALYSES] Manipulation Check 

```{r,echo=FALSE}

# Subset only necessary variables
bds.data.WRSR.KSS <-bds.data.WRSR[c("PtID", "SessionTime", "Condition", "StartKSS")]

# Keep unique values
bds.data.WRSR.KSS <- distinct(bds.data.WRSR.KSS)


```

### Normality check of StartKSS variable
```{r,echo=FALSE}

# Density plot
plot.bds.KSS.density <- ggplot(bds.data.WRSR.KSS, aes(x = StartKSS)) + geom_density()

# Shapiro-Wilk test   
shapiro.test(bds.data.WRSR.KSS$StartKSS)

# ---------------------------------------------------------------------
# Both density plots and Shapiro-wilk test indicate non-normality
# APPLY NON-LINEAR TRANSFORMATIONS
# ---------------------------------------------------------------------

# Square-root transformation
bds.data.WRSR.KSS$sqrtKSS <- sqrt(bds.data.WRSR.KSS$StartKSS)

# inspect plot
plot.bds.sqrtKSS.density <- ggplot(bds.data.WRSR.KSS, aes(x = sqrtKSS)) + geom_density()

# Shapiro test
shapiro.test(bds.data.WRSR.KSS$sqrtKSS)

# Though the Shapiro-wilk test is still significant, the density plot shows that the square-root transformation has alleviated the normality issue. 

```



### Create model

```{r,echo=FALSE}

# Create model
m.bds.KSS <- lmer(StartKSS ~ 1 + SessionTime*Condition + (1|PtID),
               data = bds.data.WRSR.KSS)

m.bds.KSS1 <- lmer(StartKSS ~ 1 + SessionTime + Condition + (1|PtID),
               data = bds.data.WRSR.KSS)
m.bds.KSS2 <- lmer(StartKSS ~ 1 + SessionTime*Condition + (1|PtID),
               data = bds.data.WRSR.KSS)

anova(m.bds.KSS1, m.bds.KSS2)

# Follow up models using separate AM and PM data
bds.data.WR.KSS <- bds.data.WRSR.KSS[bds.data.WRSR.KSS$Condition == "WR",]
bds.data.SR.KSS <- bds.data.WRSR.KSS[bds.data.WRSR.KSS$Condition == "SR",]

# Model of AM only
m.bds.KSS.WR <- lmer(StartKSS ~ 1 + SessionTime + (1|PtID),
                     data = bds.data.WR.KSS)

m.bds.KSS.SR <- lmer(StartKSS ~ 1 + SessionTime + (1|PtID),
                     data = bds.data.SR.KSS)


summary(m.bds.KSS); lm.beta.lmer(m.bds.KSS); confint(m.bds.KSS, method = "Wald")

# Get R-squared
r.squaredGLMM(m.bds.KSS)

# Check collinearity
check_collinearity(m.bds.KSS)

# Model output in APA style
tab_model(m.bds.KSS,
          show.est = TRUE,
          show.se = TRUE,
          string.se = "SE",
          string.ci = "95% CI",
          string.est = "Estimate"
          )
```

#### Inspect Residuals via Residual plots

```{r,echo=FALSE}
sim_output <- simulateResiduals(m.bds.KSS, plot = F); plotQQunif(sim_output); plotResiduals(sim_output)

```

#### Plot the graphs of KSS least-square estimates

``` {r, echo = FALSE}

# lsmeans of pooled model with SessionTime x Condition interaction [do not use]
bds.data.KSS.lsmeans <- as_tibble(
  lsmeans(m.bds.KSS, spec = c("Condition", "SessionTime", by = c("SessionTime")
                           ))
  )

# Get lsmeans from each follow-up model
bds.data.WR.KSS.lsmeans <- as_tibble(
  lsmeans(m.bds.KSS.WR, spec = "SessionTime")
  ) %>% mutate(Condition = "WR")
bds.data.SR.KSS.lsmeans <- as_tibble(
  lsmeans(m.bds.KSS.SR, spec = "SessionTime")
) %>% mutate(Condition = "SR")

# Bind into one tibble
bds.data.KSS.lsmeans <- rbind(bds.data.WR.KSS.lsmeans, bds.data.SR.KSS.lsmeans)%>% mutate(Condition = factor(Condition, levels = c("WR", "SR")))


bds.plot.KSS.lsmeans <- ggplot(bds.data.KSS.lsmeans, aes(x = SessionTime, y = lsmean, group = Condition)) +
  geom_line(aes(color = Condition)) +
  geom_point(size = 2 , aes(color= Condition)) +
  scale_color_manual(values = c("blue", "red")) +
  scale_shape_manual(values = c(17, 19)) +
  scale_y_continuous(limits = c(2, 7)) +
  geom_errorbar(aes(ymin = bds.data.KSS.lsmeans$lower.CL, ymax = bds.data.KSS.lsmeans$upper.CL, color = Condition),  width = 0.1) + 
  theme_classic() + 
  theme(
    aspect.ratio = 0.9, 
    axis.title = element_text(size = 18), axis.text = element_text(size = 15), 
    axis.line = element_line(colour = 'black', linewidth = 2),
    legend.title = element_text(size = 15), legend.text = element_text(size = 12)
    )


# fill = c("#999DA0", "#777B7E", "#C7C6C1")
bds.plot.KSS.lsmeans <- ggplot(bds.data.KSS.lsmeans, aes(x = SessionTime, y =  lsmean, fill= Condition, label = lsmean)) +
  geom_bar( position = position_dodge(), stat = "identity", color = "black", linewidth = 1) +
  
  scale_fill_manual(values = c("#F1F1F1", "#7B7B7B")) +
  scale_y_continuous(limits = c(0, 8)) +
  labs(x = "Session Time", y = "KSS score") + 
  geom_errorbar(aes(ymin = bds.data.KSS.lsmeans$lower.CL, ymax = bds.data.KSS.lsmeans$upper.CL), color = "#222021", width = 0.2, linewidth = 1, position = position_dodge(.9))+
  theme_classic() + 
  theme(aspect.ratio = 0.9, axis.line = element_line(colour = 'black', linewidth = 2), axis.title = element_text(size = 18), axis.text = element_text(size = 15), legend.title  = element_text(size = 15), legend.text = element_text(size = 12)) 
  # geom_text(aes(label = round(lsmean, 2)), position = position_dodge(1), vjust = -5, size = 5.5)

# Save as png with transparent background
ggsave(
  plot = bds.plot.KSS.lsmeans,
  filename = "img/bds/BDS_KSS_score.png",
  bg = "transparent"
  )


```


## [ANALYSES] Accuracy Check

```{r,echo=FALSE}

# Create Order variable to represent no. of times participant has done the task
bds.data.WRSR.exNB$Order <- ifelse(bds.data.WRSR.exNB$NormalFirst == 1 & bds.data.WRSR.exNB$SessionTime == "AM", 1,
                                   ifelse(bds.data.WRSR.exNB$NormalFirst == 1 & bds.data.WRSR.exNB$SessionTime == "PM", 2, 
                                          ifelse (bds.data.WRSR.exNB$NormalFirst == 0 & bds.data.WRSR.exNB$SessionTime == "AM", 3 , 4)))

# Accuracy model excluding NoBrainer trials
m.bds.ACC1<-glmer(
  IsCorrect~ 1 + Order + Condition + SessionTime + (1|PtID),
  family = binomial("logit"),
  bds.data.WRSR.exNB
  );

m.bds.ACC2<-glmer(
  IsCorrect~ 1 + Order + Condition*SessionTime + (1|PtID),
  family = binomial("logit"),
  bds.data.WRSR.exNB
  );

anova(m.bds.ACC1, m.bds.ACC2)

# Get R-squared
r.squaredGLMM(m.bds.ACC)

# Check collinearity
check_collinearity(m.bds.ACC)


# Model output in APA style
tab_model(
  m.bds.ACC,
  # show.est = TRUE,
  show.se = TRUE,
  string.se = "SE",
  string.ci = "95% CI",
  string.est = "Estimate",
  digits = 3
  );

# Get accuracy least-square estimates
bds.data.ACC <- lsmeans(m.bds.ACC1, 
                                spec = c("Condition", "SessionTime"),  
                                by = c("Condition"), type = "response"
                                );

bds.data.ACC <- as_tibble(bds.data.ACC);   # Coerce to tibble


# Plot accuracy least-square estimates
plot.bds.ACC <- ggplot(bds.data.ACC, aes(x = Condition, y = prob, color = SessionTime )) + 
  geom_point(size = 3) +
  scale_y_continuous(limits = c(0.5, 1)) +
  labs( x = "Condition", y = "Probability of Accurate Response", color = "Session") +
  scale_color_manual(values = c("black", "black")) + 
  geom_errorbar(aes(ymin = bds.data.ACC$asymp.LCL, ymax = bds.data.ACC$asymp.UCL), color = '#595959', width = 0.1) + 
  theme_bw()+
  theme(aspect.ratio = 1.5, axis.title = element_text(size=18), axis.text=element_text(size=15),
        legend.title=element_text(size=15), legend.text=element_text(size =12))



# Facet wrap the plot
plot.bds.ACC <- plot.bds.ACC + facet_wrap(~SessionTime, ncol = 2) +theme(strip.text = element_text(size = 15));  

# Save as png with transparent background
ggsave(
  plot = plot.bds.ACC,
  filename = "img/bds/BDS_trial_accuracy.png",
  bg = "transparent"
  )

 
```

### Check Residuals

```{r,echo=FALSE}
sim_output <- simulateResiduals(m.bds.ACC, plot = F); plotQQunif(sim_output); plotResiduals(sim_output)

```
---

# [ANALYSES] PROBIT MODELS

## Analyses Excluding NoBrainer Trials

### Pooled SR Model without the NoBrainer trials 

Note: Convergence issue on this model
```{r,echo=FALSE}

m.bds.WRSR.AMPM.exNB <- glmer(
  PtResp ~ 1 + SessionTime*Condition*LogLLA + SessionTime*Condition*LogBaserate + (1|PtID),
  family = binomial('probit'),
  # control = glmerControl(boundary.tol = 1e10, tolPwrss = 5e-2), # Optional line to adjust tolerance, but not sure if statistically viable
  data = bds.data.WRSR.exNB
)

# Convergence error message:
## Warning in checkConv(attr(opt, "derivs"), opt$par, ctrl = control$checkConv,  :
##   Model failed to converge with max|grad| = 0.00726695 (tol = 0.002, component 1)

```
### AM-only model without NoBrainers 

```{r,echo=FALSE}



# Build the probit model

m.bds.WRSR.AM.exNB <- glmer(PtResp ~ 1 + Condition*LogLLA + Condition*LogBaserate + 
                  (1 |PtID),
             family = binomial(link = 'probit'),
             bds.data.WRSR.AM.exNB
             )

# Print summary and confint
summary(m.bds.WRSR.AM.exNB); confint(m.bds.WRSR.AM.exNB, method="Wald",level = 0.95, oldNames="FALSE")
# Get R-squared
r.squaredGLMM(m.bds.WRSR.AM.exNB)
# Check collinearity
check_collinearity(m.bds.WRSR.AM.exNB)

# Model output in APA style
tab_model(
  m.bds.WRSR.AM.exNB,        
  transform = NULL, show.est = TRUE, show.se = TRUE,
  string.se = "SE", string.ci = "95% CI", string.est = "Estimate",
  digits = 3, digits.p = 3, digits.rsq = 3, digits.re = 3
  );

# [EXPERIMENTAL] Create scaled variables for LogLLA and LogBaserate on the standard deviation scale
bds.data.WRSR.AM.exNB$LogLLA_scaled      <- scale(bds.data.WRSR.AM.exNB$LogLLA)
bds.data.WRSR.AM.exNB$LogBaserate_scaled <- scale(bds.data.WRSR.AM.exNB$LogBaserate)

```

#### Check Residuals
```{r,echo=FALSE}
sim_output <- simulateResiduals(m.bds.WRSR.AM.exNB, plot = F); plotQQunif(sim_output); plotResiduals(sim_output)

```

### Decision Weight Analyses
```{r,echo=FALSE}

# Chi-square tests between coefficients
linearHypothesis(m.bds.WRSR.AM.exNB, 
                 c(" LogBaserate =  LogLLA"),                             # WR coefficients
                 rhs=NULL, vcov.=NULL, singular.ok=FALSE, verbose=FALSE)

linearHypothesis(m.bds.WRSR.AM.exNB, 
                 c(" ConditionSR:LogBaserate =  ConditionSR:LogLLA"),     # Interaction coefficients to determine if extent of change is sig. different
                 rhs=NULL, vcov.=NULL, singular.ok=FALSE, verbose=FALSE)



```

### Calculate and plot Relative Decision Weights for AM session
```{r,echo=FALSE}


# Calculate relative decision-weights

LogLLA         <- 0.30879 
LogBaserate    <- 0.77677 
SR_LogLLA      <- LogLLA + -0.06359
SR_LogBaserate <- LogBaserate + -0.12544



WR.AM.RDW   <- calculate_relative_dw(LogLLA, LogBaserate)
SR.AM.RDW   <- calculate_relative_dw(SR_LogLLA, SR_LogBaserate)

condition   <- c("WR_AM", "SR_AM")
relative_dw <- c(WR.AM.RDW, SR.AM.RDW)

# Create tibble with condition and their respective RDWs
bds.data.AM.RDW           <- tibble(condition, relative_dw);
bds.data.AM.RDW$condition <- factor(bds.data.AM.RDW$condition, levels = c("WR_AM", "SR_AM"));


# Plot the decision
         
plot.bds.AM.RDW <- ggplot(data=bds.data.AM.RDW, aes(x = condition, y = relative_dw)) + 
  geom_bar(
    stat ="identity", width = 0.4, fill= c("#D3D3D3", "#7B7B7B"), color = c("black", "black")
    ) +
  xlab("Condition") + ylab("") +                     # Rename x and y axes
  geom_hline(yintercept = 0, linetype = 'solid') +  # adds line on y_intercept = 0
  scale_y_continuous(limits = c(-.6, .6))+              # set y axis limits
  labs(title = "AM Session", y = "Relative Decision Weight", x = "Condition")   +       # add title and axis title
  # geom_text(aes(label = round(relative_dw, 2)), nudge_y = -0.04)+  # add text values of each bars
  #geom_signif(comparisons = list(c("WR_AM", "SR_AM")), annotations = "N.S.", y_position = .1) + # Add significance lines
  theme_bw() + theme(aspect.ratio =  1.5, axis.text = element_text(size = 15) ,axis.title=element_text(size=18), plot.title=element_text(size=18)) +
  scale_x_discrete(labels = c("WR", "SR"))

# Remove placeholder variables from global
rm(LogLLA); rm(LogBaserate); rm(WR.AM.RDW); rm(SR.AM.RDW); rm(SR_LogLLA); rm(SR_LogBaserate); rm(condition); rm(relative_dw);

```

## PM-only model without NoBrainers 
```{r,echo=FALSE}

# Create model
m.bds.WRSR.PM.exNB <- glmer(
  PtResp ~ 1 + Condition*LogLLA + Condition*LogBaserate + (1|PtID),
  family = binomial('probit'),
  bds.data.WRSR.PM.exNB
  );




# Print summary & confint
summary(m.bds.WRSR.PM.exNB); confint(m.bds.WRSR.PM.exNB, method = "Wald");

# Check collinearity
check_collinearity(m.bds.WRSR.PM.exNB)

# Confidence Intervals
confint(m.bds.WRSR.PM.exNB, method="Wald",level = 0.95, oldNames="FALSE")


# Model output in APA style
tab_model(m.bds.WRSR.PM.exNB,
          transform = NULL, show.est = TRUE, show.se = TRUE,
          string.se = "SE", string.ci = "95% CI", string.est = "Estimate",
          digits = 3, digits.p = 3, digits.rsq = 3, digits.re = 3
          );




```

### Check Residuals
```{r,echo=FALSE}

# Check residuals
sim_output <- simulateResiduals(m.bds.WRSR.PM.exNB, plot = F); plotQQunif(sim_output); plotResiduals(sim_output)

```

### Decision Weight Analyses
```{r,echo=FALSE}

# Chi-square tests
linearHypothesis(m.bds.WRSR.PM.exNB, c(" LogBaserate =  LogLLA"), rhs=NULL,
                 vcov.=NULL, singular.ok=FALSE, verbose=FALSE)

linearHypothesis(m.bds.WRSR.PM.exNB, c(" ConditionSR:LogBaserate =  ConditionSR:LogLLA"), rhs=NULL,
                 vcov.=NULL, singular.ok=FALSE, verbose=FALSE)



```


### Calculate and plot Relative Decision Weights for PM session

``` {r, echo = FALSE}

# Calculate relative decision-weights

LogLLA           <- 0.29171 ;
LogBaserate      <- 0.72799;


RDW_WR  <- calculate_relative_dw(.29171, .72799)
RDW_SR  <- calculate_relative_dw(.29171 -.05820, .72799 + .04367)

condition    <- c("WR_PM", "SR_PM")
RDW          <- c(RDW_WR, RDW_SR)


# Create tibble
bds.temp.PM.RDW <- tibble(condition, RDW)
bds.temp.PM.RDW$condition = factor(bds.temp.PM.RDW$condition, levels = c("WR_PM", "SR_PM")) # Factorise condition


# Plot the Relative Decision Weights
plot.bds.PM.RDW <- ggplot(data = bds.temp.PM.RDW, aes(x = condition, y = RDW)) + 
  geom_bar(stat ="identity", width = 0.4, fill= c("#D3D3D3", "#7B7B7B"), color = c("black", "black")) +
  xlab("Condition")  +    # Rename x and y axes
  geom_hline(yintercept = 0, linetype = 'solid') +  # adds line on yintercept = 0
  scale_y_continuous(limits = c(-.6,.6))+   # set y axis limits
  labs(title = "PM Session", y = "") +  # add title
  # geom_text(aes(label = round(RDW, 3)), nudge_y = -0.04)+  # add text values of each bars
  #geom_signif(comparisons = list(c("WR_AM", "SR_AM")), annotations = "N.S.", y_position = .1) + # Add significance lines
  theme_bw() + theme(aspect.ratio =  1.5, axis.text = element_text(size = 15), axis.title=element_text(size=18), plot.title= element_text(size = 18)) +
  scale_x_discrete(labels = c("WR", "SR"))

  
# Place AM and PM RDW plots side by side in one single figure
plot.bds.all.RDW <- ggarrange(plot.bds.AM.RDW, plot.bds.PM.RDW, ncol = 2 , nrow = 1)


# Save as png with transparent background
ggsave( plot = plot.bds.all.RDW,
        filename = "img/bds/BDS_relativeDecisionWeights.png",
        bg = "transparent")


# Remove placeholder variables from global
rm(LogLLA);rm(LogBaserate);rm(RDW_SR);rm(RDW_WR);rm(condition);rm(RDW);rm(bds.temp.PM.RDW);

```


---
## Plot Decision Weights across both AM & PM sessions

```{r, echo = FALSE}

# Create placeholder variables and fill with respective data
condition    <- c("WR", "WR", "SR", "SR", "WR", "WR", "SR", "SR");
session      <- c(rep("AM", 4), rep("PM", 4));
information  <- c(rep(c("Evidence", "Base Rate"), 4));

coefficients <- c(0.30879,  0.77677,  0.2452,  0.65133,  0.29171,  0.72799,  0.23351,  0.77166);

se_lower     <- c(0.28761,  0.73181,  0.21407,  0.58405,  0.27113,  0.6843,  0.20264,  0.70358);
se_upper     <- c(0.32997,  0.82173,  0.27633,  0.71861,  0.31229,  0.77168,  0.26438,  0.83974);
ci_lower     <- c(0.2672815, 0.6886429, 0.1841902, 0.5194604, 0.25137681, 0.64235532, 0.17300985, 0.63821854);
ci_upper     <- c(0.350304, 0.864895588, 0.306202423, 0.783197672, 0.332046028, 0.813631264, 0.294015979, 0.905105997);

# Create tibble for Decision Weights
bds.temp.DW  <- tibble(condition, session, information, coefficients, se_lower, se_upper, ci_lower, ci_upper)

bds.temp.DW$condition   <- factor(bds.temp.DW$condition, levels = c("WR","SR"))
bds.temp.DW$session     <- factor(bds.temp.DW$session, levels = c("AM", "PM"))
bds.temp.DW$information <- factor(bds.temp.DW$information, levels = c("Base Rate", "Evidence"))

plot.bds.DW <- ggplot(data = bds.temp.DW, aes( x = condition, y = coefficients , shape =  information)) + 
  geom_point(size= 3) + 
  scale_y_continuous(limits = c(0, 1)) +
  scale_shape_manual(values = c(17, 19))+
  # scale_color_manual(labels = c("Draw Outcome","Base Rate Odds"), values = c("blue", "red"))+
  labs(x = "Condition", y = "Decision Weight", shape = "Information")+
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),linewidth = 1, color = '#595959', width = 0.1)+ # Add error bars
  theme_bw(base_size = 18) + 
  theme(aspect.ratio =  2,  axis.title = element_text(size=15), axis.text=element_text(size=15),
        legend.text=element_text(size=15), legend.title = element_text(size = 15))  

# Facet wrap plots
plot.bds.DW <- plot.bds.DW  + facet_wrap(~session, ncol = 2) + theme(strip.text = element_text(size = 15), panel.border = element_rect(size = 2));


# Save as png with transparent background
ggsave( plot = plot.bds.DW,
        filename = "img/bds/BDS_decisionWeights.png",
        bg = "transparent")

# Remove placeholder variables
rm(condition);rm(session);rm(information);rm(coefficients);rm(se_lower);rm(se_upper);rm(ci_lower);rm(ci_upper);rm(bds.temp.DW)

```

## Check proportion of easy to hard trials (Easy trials are those with post_prob >.8 or <.2)

Number of Easy trials = 1781
Number of Hard trials = 1999
Proportion that are easy = 47.11%

# END

